---
title: "Day2_Activity_Arora"
author: "Raghav Arora"
date: "2022-09-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries}
library(tidyverse)
library(here)
library(ggplot2)
```

```{r data_read}
data <- read.csv(here("colleges_clean.csv"))
```

# Questions and Answers

1.  How many private and public schools are there in your data?

```{r Q1}
data %>%
  ggplot(aes(x=CONTROL))+
  geom_bar()
```

Ans. Public: 500 schools, Private: 800 schools

2.  What is the overall average SAT Score?

```{r Q2}
data %>%
  ggplot(aes(x=SAT_AVG))+
  geom_histogram()
```

Ans. Avg: 1100

3.  What is the average SAT score for Private and Public schools?

```{r Q3}
data_c <- data %>%
  mutate(CONTROL = ifelse(CONTROL == 1, "Public","Private")) 
data_c %>%
  ggplot(aes(x=SAT_AVG, fill=CONTROL))+
  geom_histogram()
```

Ans. Private Avg: 1150 , Private Avg: 1050

4.  Which school has the largest difference betweeen In- and Out-of-State tuition?

```{r Q4}
data_2 <- data %>%
  slice_max(TUITION_DIFF, n=5)
ggplot(data=data_2)+
  geom_col(mapping=aes(x=TUITION_DIFF, y=INSTNM, fill=INSTNM))
```

Ans. University of Michigan Ann Arbor has the highest tuition difference.

5.  Are "better" schools more expensive?

```{r Q5}
data$TUITION_AVG = (data$TUITIONFEE_IN+data$TUITIONFEE_OUT)/2
data %>%
  ggplot(aes(x=SAT_AVG, y=TUITION_AVG))+
  geom_point()
```

Ans. Colleges with students with higher SAT averages ('better') generally tend to be more expensive.

6.  Which states tend to have the "best deals" of colleges?

```{r Q6}
data_3 <- data %>%
  group_by(STABBR) %>%
  summarise(TUITION_AVG = mean(TUITION_AVG), SAT_avg = mean(SAT_AVG))

ggplot(data = data_3) +
  geom_point(mapping = aes(x=TUITION_AVG, y = SAT_avg, color = STABBR)) 

data_4 <- data_3 %>% 
  slice_min(TUITION_AVG,n = 10)

ggplot(data = data_4) +
  geom_point(mapping = aes(x=TUITION_AVG, y = SAT_avg, color = STABBR)) 
```

Ans. Wyoming (WY) has the best deal since it has a high sat average and comparatively low tuition average.

7.  Do different regions have different public and private school distributions?

```{r Q7}
data_c %>%
  ggplot(aes(x=factor(REGION), fill=CONTROL), position = "fill") +
  geom_bar()
```

Ans. Every region has different distributions except for region 0 and 9 which only have public schools.

8.How does the size of the school relate to the cost, correcting for public versus private status?

```{r Q8}
data_c <- data %>%
  mutate(CONTROL = ifelse(CONTROL == 1, "Public","Private")) 
data_c %>%
  ggplot(aes(x=TUITION_AVG, y=UGDS,color=CONTROL))+
  geom_point()
```

Ans. For PRIVATE schools, as the tuition fee increases, the size of the school increases gradually. 
For PUBLIC schools, as the tuition fee increases, the size of the school increases exponentially.

Plot Re-creation:

```{r Plot Re}
data_c <- data %>%
  mutate(CONTROL = ifelse(CONTROL == 1, "Public","Private")) 
data_c %>%
  ggplot(aes(x=factor(REGION), y=ADM_RATE,fill=CONTROL))+
  geom_boxplot()
```
